О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
Proofreading by Usachev - p. 10

	So, $M = \{ M_{J\pm}, N\}$ is indeed a planar integral point set of $2^k+1$ points,
	and distance 1 occurs in $M$.
	Reminding that $k$ can be taken arbitrary large, we conclude that we can construct
	a planar integral point set of arbitrary large cardinality so that the distance 1 occurs in that set.
\end{construction}

\begin{remark}
	\label{rem:planar_set_with_minimeter_1_of_3_points}
	Applying Construction~\ref{con:planar_set_with_minimeter_1} to $k=1$ naively,
	we get $a = 3$, $I=\varnothing$, $b_\varnothing = -1$ and then
	obtain a right triangle of side length 1.
	This triangle is obviously the optimal set in $\mathfrak{M}(2,3)$.
\end{remark}

\begin{remark}
	\label{rem:planar_set_with_minimeter_1_of_4_and_5_points}
	For $k=2$ in Construction~\ref{con:planar_set_with_minimeter_1},
	we obtain the optimal set in $\mathfrak{M}(2,5)$ presented in~\cite[Fig. 1]{harborth1993upper}.
	If we truncate one point from it,
	then we get one of the two optimal sets in $\mathfrak{M}(2,4)$.
\end{remark}

@@

If the take $k=1$ in Lemma~\ref{lem:2k-1_segments},
we obtain the following result (which is exactly~\cite[Lemma 3]{our-vmmsh-2018}).
\begin{corollary}
	\label{cor:only_one_distance_1_on_straight_line}
	Let $M \in \mathfrak{M}(2,\mathbb{N})$ and let $m$ be a straight line.
	Then there is at most one pair of points $M_1,M_2\in M \cap m$
	such that $|M_1 M_2| = 1$.
\end{corollary}

To describe all the sets $M \in \mathfrak{M}(2,n)$ with distance 1,
we will need~\cite[Proposition 6]{our-vmmsh-2018}.
For the sake of completeness, we will give here a slightly rephrased version of it with the proof as the following lemma.
\begin{lemma}
	\label{lem:no_4_points_in_semigeneral_position_with_distance_1}
	Let $M=\{M_1,M_2,M_3,M_4\}\in \mathfrak{M}(2,4)$ such that $|M_1 M_2|=1$
	and let $l$ be the straight line containing points $M_1$ and $M_2$.
	Then one of the points $M_3$ or $M_4$ belongs to $l$.
\end{lemma}

@@

\begin{problem}
	\label{prb:minimal_shape}
	What is the minimal shape $\mathcal{S}$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in  $\mathcal{S}$?
\end{problem}
This problem is another generalization of Lemma~\ref{lem:square_container}.
We know that $\mathcal{S}$ is not a circle of diameter $d$
(the counterexample is a right triangle of side length $d$)
and we conjecture that $\mathcal{S}$ is not a Reuleaux triangle of width $d$
(the probable counterexample belongs to a circle of diameter $d$, see Theorem~\ref{thm:rational_set_on_circle}).

>>>>

	So, $M = \{ M_{J\pm}, N\}$ is indeed a planar integral point set of $2^k+1$ points,
	and distance 1 occurs in $M$.
	Since $k$ can be taken arbitrary large, it follows that we can construct
	a planar integral point set of arbitrary large cardinality so that the distance 1 occurs in that set.
\end{construction}

\begin{remark}
	\label{rem:planar_set_with_minimeter_1_of_3_points}
	Applying Construction~\ref{con:planar_set_with_minimeter_1} to $k=1$ naively,
	we get $a = 3$, $I=\varnothing$, $b_\varnothing = -1$ and then
	obtain an equilateral triangle of side length 1.
	This triangle is obviously the optimal set in $\mathfrak{M}(2,3)$.
\end{remark}

\begin{remark}
	\label{rem:planar_set_with_minimeter_1_of_4_and_5_points}
	For $k=2$ in Construction~\ref{con:planar_set_with_minimeter_1},
	we obtain the optimal set in $\mathfrak{M}(2,5)$ presented in~\cite[Fig. 1]{harborth1993upper}.
	If we remove one point from it,
	then we get one of the two optimal sets in $\mathfrak{M}(2,4)$.
\end{remark}

@@

Setting $k=1$ in Lemma~\ref{lem:2k-1_segments},
we obtain the following result (which is exactly~\cite[Lemma 3]{our-vmmsh-2018}).
\begin{corollary}
	\label{cor:only_one_distance_1_on_straight_line}
	Let $M \in \mathfrak{M}(2,\mathbb{N})$ and let $m$ be a straight line.
	Then there is at most one pair of points $M_1,M_2\in M \cap m$
	such that $|M_1 M_2| = 1$.
\end{corollary}

In order to describe all the sets $M \in \mathfrak{M}(2,n)$ with distance 1,
we need~\cite[Proposition 6]{our-vmmsh-2018}.
For the reader's convenience, we will state a slightly rephrased version of it and provide the proof.
\begin{lemma}
	\label{lem:no_4_points_in_semigeneral_position_with_distance_1}
	Let $M=\{M_1,M_2,M_3,M_4\}\in \mathfrak{M}(2,4)$ such that $|M_1 M_2|=1$.
	If $l$ is the straight line through points $M_1$ and $M_2$,
	then one of the points $M_3$ or $M_4$ belongs to $l$.
\end{lemma}

@@

\begin{problem}
	\label{prb:minimal_shape}
	What is the minimal shape $\mathcal{S}$ such that any $M\in\mathfrak{M}(2,\mathbb{N})$ with $\operatorname{diam} M = d$
	is situated in  $\mathcal{S}$?
\end{problem}
This problem is another generalization of Lemma~\ref{lem:square_container}.
We know that $\mathcal{S}$ is not a circle of diameter $d$
(the counterexample is an equilateral triangle of side length $d$)
and we conjecture that $\mathcal{S}$ is not a Reuleaux triangle of width $d$
(the probable counterexample belongs to a circle of diameter $d$, see Theorem~\ref{thm:rational_set_on_circle}).
